Refining character relationships using embeddings of textual units

### 2022-09-06 article/paper1.tex
write article

There exists various ways to use these pre-trained word vectors in order to find vectors for a \emph{group of words}, such as sentences (REF), paragraphs (REF), or documents (REF), which are often used to apply a classification or clustering algorithm on the newly embedded objects (REF). Here, we use a recent methodology proposed in (REF), in order to obtain textual unit vectors laying in the same space as words.

More precisely, we use a pre-trained word vectors $w_1, \ldots, w_m$ trained on Common Crawl and Wikipedia using fastText.\footnote{\url{ https://fasttext.cc/docs/en/crawl-vectors.html}, accessed September 2022.} For French, the number of word-vectors $m$ is

@@

%%
%% Define the bibliography file to be used
\bibliography{charnet}

>>>>

There exists various ways to use these pre-trained word vectors in order to find vectors for a \emph{group of words}, such as sentences (REF), paragraphs (REF), or documents (REF). These vectors are often used to apply a classification or clustering algorithm on the newly embedded objects (REF), or to query information (REF). These methods often use the frequencies of words found in the objects, i.e. a table similar to $\mathbf{N}$, but apply various weighting scheme and normalization in order to reduce the effects of frequent words and align vectors. In the present article, we use a recent methodology proposed in (REF) as it is compatible with multiple unit size and gives state-of-the-art results in multiple tasks.

More precisely, we use a pre-trained word vectors $\mathbf{w}_1, \ldots, \mathbf{w}_m$ trained on Common Crawl and Wikipedia using fastText.\footnote{\url{ https://fasttext.cc/docs/en/crawl-vectors.html}, accessed September 2022.} For French, the number of word-vectors $m$ is 2 millions and the dimension of vectors are $300$. Textual units vectors $\mathbf{x}_1, \ldots, \mathbf{x}_n$ are obtained through the table $\mathbf{N}$ and with the method detailed in Appendix \ref{wv_details}.

@@

\subsection{Unit embedding based of pre-trained word vectors}
\label{wv_details}

This methods is justified and detailed in (REF). Let $\mathbf{w}_1, \ldots, \mathbf{w}_v$ be pre-trained word vectors which appear in the studied corpus, and the $(n \times v)$ table $\mathbf{N}$ counting the frequency of these words in the $n$ textual units. We first construct the \emph{uncentered vectors} $\widetilde{\mathbf{x}}_i$ of each unit $i$ with
\begin{equation}
\widetilde{\mathbf{x}}_i = \sum_{j = 1}^v \frac{n_{ij}}{n_{i \bullet}} \frac{a}{a + \frac{n_{\bullet j}}{n_{\bullet \bullet}}} \mathbf{w}_j,
\end{equation}
where $a > 0$ is an hyperparameter which gives less importance to frequent words as $a \to 0$. Let $\widetilde{\mathbf{X}}$ be the matrix whose columns are vectors $\widetilde{\mathbf{x}}_i$, and $\mathbf{u}$ be its first singular vector. We find \emph{vectors} $\mathbf{x}_i$ of each units $i$ with
\begin{equation}
\mathbf{x}_i = \widetilde{\mathbf{x}}_i - \mathbf{u}\mathbf{u}^\top \widetilde{\mathbf{x}}_i.
\end{equation}
This last equation act like a \emph{centration} of unit vectors.
%%
%% Define the bibliography file to be used
\bibliography{charnet}
